Ms Habitat aves

### 2020-09-28 Ms_HabitatAves.Rmd
Correccion de abundancias por sitio por dia en base a probabilidad de deteccion.

[Provide brief overview of key research projects in this area]
More than the half of the cities in the world are coastal cities

@@

[General overview of this section]
In this research we conducted bird survey in six coastal urban environments in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile

[Provide background information and justification]
Each environment was defined in terms its proximity to the coast, level of anthropotization and land cover (Table 1)
We used occupancy modeling to provide information about bird habitat use, taking into account probability of detection.

[Provide an overview of the procedure/method itself]
To compare bird commmunities and species identity in them, we used ordination models

@@

[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]

@@

[Provide more detailed information about the method and show that was a good choice]

@@

##### Study area

Study area comprehends
Six habitats were identify in coastal urban areas

##### Bird surveys

##### Environmental variables

##### Seasonal GLMM

##### Occupancy modelling

##### Bird comunnity

Bird community was analysed by ordination methods with vegan package in R

>>>>

[Provide brief overview of key research projects in this area]
More than the half of the cities in the world are coastal cities and they lack of studies addressing marine. terrestrial interactions.

@@

[General overview of this section]
In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, a Metropolitan area that includes three municipalities in central Chile.

[Provide background information and justification]
Coastal environments were defined in terms of its proximity to the coast, level of anthropotization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Table 1)

[Provide an overview of the procedure/method itself]
Bird surveys were conducted in each sample site twice (winter (junio-jul) and spring (nov-dec)), 2019 given migratory species en this area, during sunrise and the three hours later for 10 minutes. 
The total of birds seing and heard was registred, in addition with the position and behavior of the bird or group of birds observed.

A characterization of environments were made throgh vegetational cover measurement and an spatial characterization with landcover information.

@@

To analyse the data, we used occupancy modeling to provide information about bird habitat use.
Occupancy variables
Detection variables
Seasonal variables

[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
To compare bird commmunities and species identity in them, we used ordination methods with vegan package in R with species abundances corrected by occupancy.
We tested significant differences among environments with an analysis of similarities (ANOSIM)

To determine species contribution to the differrence between environments we used Bray-Curtis dissimilaries with SIMPER analysis.

@@

[Provide more detailed information about the method and show that was a good choice]
Occupancy models provide a correction using detection probability mong days and colonization-extinction probability between seasons which improve ordination models

@@

**Poner en paper**
